Flexibility of interactions depends on habitat suitability

### 2019-08-29 paper/manuscript.Rmd
Write first draft of results

```{r}
loadd(bayesian_r2_baseline)
```

We found that our models performed relativelly well. 
The bayesian R-squared for our baseline model was `r round(bayesian_r2_baseline[1], digits = 2)`. 
Overall we found only weak evidence of a relationship between the environmental niche size and the normalised degree. 
We found that environmental suitability is an important variable

@@

```{r tab-model-comparison-table}
loadd(model_ranking)
waic_scores <- as.data.frame(model_ranking$waic) %>%
  tibble::rownames_to_column(var = "formula") %>%
  dplyr::select(formula, waic)

>>>>

```{r}
loadd(bayesian_r2_baseline)
loadd(parameter_posterior_summary)

random_cor <- parameter_posterior_summary %>% 
  as.data.frame() %>%
  tibble::rownames_to_column(var = "parameter") %>%
  dplyr::filter(parameter == "cor_org_id__Intercept__scaled_suitability")
```

We found that our models performed relativelly well.
The bayesian R-squared for our baseline model was `r round(bayesian_r2_baseline[1], digits = 2)`, which indicates our models were able to capture a large proporton of the variability on the data. 
Overall we found only weak evidence of a relationship between the environmental niche size and the normalised degree (Figure \@ref(fig:fig-conditional-effects)a). 
This relationship was stronger for plants than for animals.
Similarly environmental suitability does not show a consistent pattern accross species. 
Indeed, when looking at the population level effects, suitability virtually no relationship with normalised degree, neither for plants or pollinators (Figure \@ref(fig:fig-conditional-effects)b). 
However, suitability is still an important predictor as the difference between our baseline model and that that did not include suitability was XXX (±XX) (±SE). 
Both among plants and pollinators for some species there is a strong negative relationship between suitability and normalised degree and some others with a strong positive relationship (Figure \@ref(fig:fig-random-effects)a). 
The slope of this relationship was negatively correlated with the species' intercept in the model (Figure \@ref(fig:fig-random-effects)b). 
The correlation coefficient was `r round(random_cor$Estimate, 2)` with a `r round(random_cor$Q2.5, 2)` to `r round(random_cor$Q97.5, 2)` 95% credible interval.
As expected, we found a positive relationship between a species generalism and normalised degree \@ref(fig:fig-conditional-effects)c). 
However our model comparisons based on WAIC shows that including generalism in the model adds relatively little information once we have accounted for the other variables in the model.
Finally, we found a strong and positive relationship between the number of possible interactions and the number of realised interactions in the community.

Random effects SD. eviation

@@

```{r tab-model-comparison-table}
loadd(model_ranking)

waic_scores <- as.data.frame(model_ranking$waic) %>%
  tibble::rownames_to_column(var = "formula") %>%
  dplyr::select(formula, waic)
